### 2012-12-13 htdocs/anchoring.tex
Added comment and reference on Euler-Lagrange eq. for anchoring
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1834 40876441-3496-0410-a613-a2fca35b2ae2

The boundary condition we wish to apply is, for the bulk term
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}} = 0
\end{equation}
where $Q_{\alpha\beta,\gamma} = \partial_\gamma Q_{\alpha\beta}$. Here,
$n_\gamma$ is the outward unit normal at the surface (pointing into the
fluid). With the
addition of the surface term we obtain
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}}
+ \frac{\partial f_s}{\partial Q_{\alpha\beta}} = 0.
\end{equation}
The derivative of the distortion free energy with respect to
$Q_{\alpha\beta,\gamma}$ gives
\begin{equation}
\kappa_0 n_\beta \partial_\gamma Q_{\alpha\gamma}
+ \kappa_1 n_\gamma
(\partial_\gamma Q_{\alpha\beta} - \partial_\alpha Q_{\gamma\beta})
- 2\kappa_1 q_0 n_\gamma \epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}.
\end{equation}
However, if we want a symmetric form (the derivative with respect to
$Q_{\beta\alpha,\gamma}$ is just as good) we can write this as
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha}).
\end{eqnarray}
If we add the derivative of the surface free energy,
where we assume that the preferred orientation $Q_{\alpha\beta}^0$ is
independent of $Q_{\alpha\beta}$, we get a full boundary condition
for the gradient of the tensor order parameter at the solid-fluid boundary:
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w(Q_{\alpha\beta} - Q_{\alpha\beta}^0) = 0.
\label{cholesteric_bc}
\end{eqnarray}

>>>>

The boundary condition we wish to apply are the Euler-Lagrange equations. 
They are at the surface of the particle
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}} = 0
\end{equation}
where $Q_{\alpha\beta,\gamma} = \partial_\gamma Q_{\alpha\beta}$. Here,
$n_\gamma$ is the outward unit normal at the surface (pointing into the
fluid) \cite{skarabot}. Note that compared to the regular minimization as  
explained in \cite{wright} this is a surface integral term that would 
usually vanish in the bulk.
With the
addition of the surface term we obtain
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}}
+ \frac{\partial f_s}{\partial Q_{\alpha\beta}} = 0.
\end{equation}
The derivative of the distortion free energy with respect to
$Q_{\alpha\beta,\gamma}$ gives
\begin{equation}
\kappa_0 n_\beta \partial_\gamma Q_{\alpha\gamma}
+ \kappa_1 n_\gamma
(\partial_\gamma Q_{\alpha\beta} - \partial_\alpha Q_{\gamma\beta})
- 2\kappa_1 q_0 n_\gamma \epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}.
\end{equation}
However, if we want a symmetric form (the derivative with respect to
$Q_{\beta\alpha,\gamma}$ is just as good) we can write this as
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha}).
\end{eqnarray}
If we add the derivative of the surface free energy,
where we assume that the preferred orientation $Q_{\alpha\beta}^0$ is
independent of $Q_{\alpha\beta}$, we get a full boundary condition
for the gradient of the tensor order parameter at the solid-fluid boundary:
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w(Q_{\alpha\beta} - Q_{\alpha\beta}^0) = 0.
\label{cholesteric_bc}
\end{eqnarray}
